Titulo

### 2015-02-10 RotacionOutFlows/Paper/ms.tex
a couple of references

A variety of Astrophysical problems can be studied using LAEs; clustering
of galaxies at high redshift, Interstellar (ISM) and intergalactic (IGM) medium 
properties and cosmological reionization among others. This motivates to study in 
detail the processes that model the morphology of the \lya line.

To fully understand the observed spectra of LAEs this galaxies must be modeled.
however the resonant nature of the lines makea this a challenging task. 
Neufeld et 90 the outcoming spectra of galaxies through static mediums 
Recent hydrodynamical simulations have been explored the properties of the IGM/ISM 
in large scale simulations, while some others have studied detailed galaxies. 
On the other hand RT computations have been in order to understand the effect of the 
gas kinematics in the Line, special attention have been devoted to model the presence 
of outflows in the galaxy. here different models have attempt to (name the models, shell cavities etc.)
. Most recently \cite{Garavito14} have studied in detail the effect 
of rotation on the lyman alpha line.

>>>>

A variety of Astrophysical problems can be studied using LAEs; clustering
of galaxies at high redshift, Interstellar (ISM) and intergalactic (IGM) medium 
properties and cosmological reionization for a recent review see \cite{review} 
among others. This motivates to study in 
detail the processes that model the morphology of the \lya line.

To fully understand the observed spectra of LAEs this galaxies must be modeled.
however the resonant nature of the lines makea this a challenging task. 
\cite{Neufeld90} the outcoming spectra of galaxies through static mediums 
Recent hydrodynamical simulations have been explored the properties of the IGM/ISM 
in large scale simulations, while some others have studied detailed galaxies. 
On the other hand RT computations have been in order to understand the effect of the 
gas kinematics in the Line, special attention have been devoted to model the presence 
of outflows in the galaxy. here different models have attempt to (name the models, shell cavities etc.)
. Most recently \cite{Garavito14} have studied in detail the effect 
of rotation on the lyman alpha line.
